---
title: "About the Anti-Discrimination Working Group"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## Who are we? 
<br>
We are psychiatric genetics researchers at Aarhus University, based at the
<a href="https://clin.au.dk/" target="_blank" rel="noopener noreferrer" title="The Department of Clinical Medicine">Department of Clinical Medicine</a> and 
<a href="https://ncrr.au.dk/" target="_blank" rel="noopener noreferrer" title="The National Centre for Register-based Research">the National Centre for Register-based Research (NCRR)</a>. We started an Anti-Discrimination Working Group in the spring of 2023 to discuss issues related to discrimination and bias in human genetics and psychiatry research. The aim is to be better informed and more inclusive in our research.
<br><br><br>
 
## What are our aims?
<br>
We were inspired by the <a href="https://www.kcl.ac.uk/mental-health-and-psychological-sciences/about/departments/social-genetic-and-developmental-psychiatry" target="_blank" rel="noopener noreferrer" title="Social, Genetic & Developmental Psychiatry Centre, King's College London">Social, Genetic & Developmental Psychiatry Centre</a>’s Anti-Racism Working Group at King's College London. Based on the goals of their group, we defined the following aims:

* To strive for **equality**
* To strive for **diversity**
* To be **open** and **transparent**
* To be mindful that **the topics we discuss may be triggering and upsetting**, impacting on people in different ways.  

<space><space><space><space><font size = 3>This is not a passive intellectual topic. It takes time to install the correct support and find solutions. **This is a learning process**</font>

* To discuss ongoing issues with **discrimination in research**
* To recognize **harmful structures and practices** of discrimination in research
* To **advocate for changes** that promote equality in research
<br><br><br>

## Covered topics
<br>
So far, we have covered the following topics:
<br><br>
<a href="First_meeting.html" title="Kick-off meeting - Friday 31st March 2023">__The misappropriation of genetics research__</a>, 
<br>
<a href="Second_meeting.html" title="Second meeting - Wednesday 17th May 2023">__The history of eugenics as it relates to genetic research__</a>,
<br>
<a href="Third_meeting.html" title="Third meeting - Wednesday 23rd June 2023">__Polygenic embryo screening__</a>, and
<br>
<a href="Sixth_meeting.html" title="Sixth meeting - Wednesday 1st November 2023">__Ableism and positive psychology__</a>.
<br><br>
You can find a summary, slides and further information about the different meetings under the tab **Meetings**.
<br><br><br>

## Future topics
<br>
There is still an endless number of interesting topics that we could cover. Two potential topics are bioethics and genetic counselling. 
<br>

**Do you have an interesting topic that you want to discuss?**

<br> 
Then please do not hesitate to contact us!
<br><br><br>

## Join us!
<br>
Please join us for our next meeting, which will be held in **December 2023**.
If you would like to be invited to future hybrid meetings, receive reminder emails, and other information <a href="contact.html" title="Join us!">**contact** us</a>!
<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```