---
title: "8th meeting - Thursday 22nd of February 2023"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## Book club: _The Immortal Life of <b>He</b>nrietta <b>La</b>cks_
<br>
The next anti-discrimination working group meeting will be a book club, where we will discuss the book <a href="https://rebeccaskloot.com/the-immortal-life/about-the-book/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">_The Immortal Life of <b>He</b>nrietta <b>La</b>cks_</a> by Rebecca Skloot.
<br><br>

#### How to access the book?

You can buy the book <a href="https://www.saxo.com/dk/the-immortal-life-of-henrietta-lacks_rebecca-skloot_paperback_9781400052189" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks by Rebecca Skloot">here</a>.

Not a bookworm? No problem! You can also watch the <a href="https://www.imdb.com/title/tt5686132/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">movie</a>, or listen to the audiobook on <a href="https://www.amazon.com/Immortal-Life-Henrietta-Lacks/dp/B0036UZCRM" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">Audible</a> or on <a href="https://mofibo.com/dk/authors/rebecca-skloot-4268" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">mofibo</a>.
<br><br>

<!--You can find the slides (in PDF format) used in connection to this meeting <a href="Slides/ADWG_meeting8.pdf" target="_blank" rel="noopener noreferrer" title="ADWG meeting - Book club: The Immortal Life of Henrietta Lacks">here</a>-->.
<br><br><br>

## Further information:
<br>

* <a href="https://rebeccaskloot.com/the-immortal-life/about-the-book/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks by Rebecca Skloot">The Immortal Life of Henrietta Lacks</a>, Rebecca Skloot.
* <a href="http://henriettalacksfoundation.org/" target="_blank" rel="noopener noreferrer" title="The Henrietta Lacks Foundation">The Henrietta Lacks Foundation</a>


<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```