---
title: "8th meeting - Thursday 22nd of February 2024"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## Book club: _The Immortal Life of <b>He</b>nrietta <b>La</b>cks_
<br>
The second anti-discrimination working group meeting in 2024 was a book club, where we discussed the book <a href="https://rebeccaskloot.com/the-immortal-life/about-the-book/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">_The Immortal Life of <b>He</b>nrietta <b>La</b>cks_</a> by Rebecca Skloot.
<br><br>

### About the book
<br>
_The Immortal Life of <b>He</b>nrietta <b>La</b>cks_ is a non-fiction book about <b>He</b>nrietta <b>La</b>cks and the immortal cell line known as <b>HeLa</b>. The book was published by Rebecca Skloot in 2010, many years after Rebecca Skloot started conducting research on Henrietta Lacks and her family. _The Immortal Life of <b>He</b>nrietta <b>La</b>cks_ deals with ethical issues of race and class in medical research.
<br><br>

### Who was Henrietta Lacks (incorrectly also known as Henrietta Lakes or Helen Lane)?
<br>
Henrietta Lacks was born Loretta Pleasent in Roanoke, Virginia, in 1920. After her mother's death (she died giving birth to her tenth child), Henrietta Lacks was sent to live with her grandfather, Tommy Lacks, who was a tobacco farmer in Clover, Virginia. During her time in Clover, Henrietta shared a room with her cousin David "Day" Lacks. And when Henrietta was fourteen years old, she gave birth to her and Day's first son, Lawrence. Four years later, Henrietta gave birth to their second child, a daughter named Elsie. Henrietta and Day got married two years after Elsie's birth.
After moving to Baltimore, Maryland (Turner Station), Henrietta and Day received three more children; David Jr, Deborah and Joseph (later Zakariyya). Less than five month after giving birth to Joseph in November 1950, Henrietta was diagnosed with cervical cancer. After being treated with radium tube inserts and X-ray treatments (both treatments having severe side effects), Henrietta Lacks died at the Johns Hopkins hospital on October 4, 1951.
<br>
According to her family members, Henrietta loved dancing and was very caring. 
<br><br>

### A short summary of the book
<br>

* 1951: Henrietta Lacks was admitted to the “colored” section of Johns Hopkins Hospital to treat a “knot” on her cervix. She signed a consent form to get any surgery necessary to treat her cancer.
* The treating gynecologist took a sample of her cervical cells, both cancerous and healthy, and gave them to George Gey, who was collecting tissue samples from all cervical cancer patients.
* The cell culture from Henrietta’s cervical cancer cells survived and grew quickly; It was the first success in the world of human cell culturing.
* Despite surgery and radiation therapy, Henrietta’s cancer returned and quickly spread. The cancer and its treatment caused her a lot of suffering.
* Henrietta’s husband Day consented to an autopsy after her death.
* Over time, for-profit cell culture labs started mass-producing <b>HeLa</b> cells.
* To resolve issues with <b>HeLa</b> cells contaminating other cell cultures, geneticists at Hopkins contacted the Lacks children to get blood samples and identify distinct genetic markers. The Lacks children were not informed about the actual purpose; they thought the samples were taken in order to screen for cancer.
* 1975: The Lacks family was contacted by a journalist after he revealed Henrietta Lacks’ true name. Henrietta's family learned that her cells were still alive and being used for profit.
* 1994: The media attention attracted conman Sir Lord Cofield, who posed as a lawyer wanting to help the Lacks family sue Johns Hopkins Hospital.
* 1999: Rebecca Skloot tried to get in contact with the Lacks family, especially daughter Deborah, to write a book about Henrietta Lacks and the <b>HeLa</b> cell line.
* 2001: Henrietta Lacks' youngest children, Deborah and Zakariyya, ”meet” their mother’s cells in a Johns Hopkins laboratory and visit the hospital where their sister Elsie had been institutionalized, causing emotional distress.
* After visiting the hospital where Elsie spent the rest of her live, Deborah's cousin performed a religious soul cleansing ceremony to lift the burden of Henrietta’s cells from Deborah.
* Deborah decides to support her grandchildren and other family members in pursuing an education so that they can better understand what happened to Henrietta and her cells, as she herself cannot afford to get an education.
* 2009: Deborah dies as Skloot finally finishes the book.

<br>
You can find a full book summery <a href="https://www.sparknotes.com/lit/immortal-life/summary/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks Full Book Summary">here</a>.
<br><br>

### Ethical dilemmas and lessons learned
<br>
Many ethical dilemmas and their consequences are mentioned in  _The Immortal Life of <b>He</b>nrietta <b>La</b>cks_. Some of them are represented in the following table:
<br><br>

<table style="width:90%">
  <tr>
    <th style="width:20%">Ethical dilemma</th>
    <th style="width:26%">1950s</th>
    <th style="width:26%">Today</th>
    <th>Danish legistlation</th>
  </tr>
  <tr>
    <td>__Informed consent__</td> <!-- Table Data (cell) -->
    <td>There was no established practice for informed or obtained consent from cell or tissue donors.</td>
    <td>The participation of human subjects in a research study requires their informed consent. A declaration of consent and any accompanying additional participant information must be formulated in a language that enables persons being asked to provide their consent to understand what they are consenting to.</td>
    <td> In Denmark, cells and tissues may be collected and stored for research without explicit consent.</td>
  </tr>
  <tr>
    <td>__Medical records privacy__</td> <!-- Table Data (cell) -->
    <td>Patients had no right to see or retain a copy of their medical records. No laws prohibited the sharing of medical record information in connection with research.</td>
    <td>Patients have the right to see and have a copy of their medical records. Laws regulate patient consent and the use and sharing of medical record information.</td>
    <td> In Denmark, health data can be used for research without explicit consent. Patients cannot obtain information about the specific analyses or projects their data was in.</td>
  </tr>
  <tr>
    <td>__Communication with tissue donors and research participants__</td> <!-- Table Data (cell) -->
    <td>There was no established practice for informed or obtained consent from cell or tissue donors.</td>
    <td>Strict patient consent processes for those who donate tissue and cellular materials for research are in place.</td>
    <td> Same left cell </td>
  </tr>
</table>

<br><br>

#### How to access the book
<br>
You can buy the book <a href="https://www.saxo.com/dk/the-immortal-life-of-henrietta-lacks_rebecca-skloot_paperback_9781400052189" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks by Rebecca Skloot">here</a>.
<br><br>
Not a bookworm? No problem! You can also watch the <a href="https://www.imdb.com/title/tt5686132/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">movie</a>, or listen to the audiobook on <a href="https://www.amazon.com/Immortal-Life-Henrietta-Lacks/dp/B0036UZCRM" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">Audible</a> or on <a href="https://mofibo.com/dk/authors/rebecca-skloot-4268" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">mofibo</a>.
<br><br>

You can find the slides (in PDF format) used in connection to this meeting <a href="Slides/ADWG_meeting8_book_club_HeLa.pdf" target="_blank" rel="noopener noreferrer" title="ADWG meeting - Book club: The Immortal Life of Henrietta Lacks">here</a>.
<br><br><br>

## Further information:
<br>

* <a href="https://rebeccaskloot.com/the-immortal-life/about-the-book/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks by Rebecca Skloot">The Immortal Life of Henrietta Lacks</a>, Rebecca Skloot.
* <a href="http://henriettalacksfoundation.org/" target="_blank" rel="noopener noreferrer" title="The Henrietta Lacks Foundation">The Henrietta Lacks Foundation</a>
* <a href="https://www.hopkinsmedicine.org/henrietta-lacks/upholding-the-highest-bioethical-standards" target="_blank" rel="noopener noreferrer" title="Upholding the highest Bioethical Standards">Upholding the Highest Bioethical Standards</a>, a statment by Johns Hopkins Medicine.
* <a href="https://doi.org/10.1146/annurev-genom-083115-022536" target="_blank" rel="noopener noreferrer" title="Lessons from HeLa Cells: The Ethics and Policy of Biospecimens">Lessons from HeLa Cells: The Ethics and Policy of Biospecimens</a>, Laura M. Beskow, in Annu Rev Genomics Hum Genet, August 2016.
* <a href="https://nationaltcenterforetik.dk/Media/637882233450564012/2015-05-12-Sundhedsdata-etiske-aspekter.pdf" target="_blank" rel="noopener noreferrer" title="Forskning i sundhedsdata og biologisk materiale i Danmark">Forskning i sundhedsdata og biologisk materiale i Danmark: Baggrundspapir – etiske aspekter</a>, Det Etiske Råd, 2015.
* <a href="https://link.springer.com/chapter/10.1007/978-3-030-49388-2_11" target="_blank" rel="noopener noreferrer" title="Balancing of Individual Rights and Research Interests in Danish Biobank Regulation">Balancing of Individual Rights and Research Interests in Danish Biobank Regulation</a>, Mette Hartlev, Part of _Law, Governance and Technology Series_ book series, January 2021.

<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```