---
title: "Kick-off meeting - Friday 31st March 2023"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## The misappropriation of genetics
<br>
The kick-off meeting focused on the misappropriation of genetics and was based on a talk by <a href="https://jedidiahcarlson.com/about/" target="_blank" rel="noopener noreferrer" title="About Jedidiah Carlson">Jedidiah Carlson</a> as well as his Twitter thread (<a href="https://twitter.com/JedMSP" target="_blank" rel="noopener noreferrer" title="Jedidiah Carlson's Twitter account">@JedMSP</a>). We highly recommend having a look at Jedidiah Carlson's Twitter thread, as he discusses important issues - such as the existence of extremist 'journal clubs', the 'meme-ification' of figures (particularly PCS plots) and the interest in research on the genetics of cognitive/behavioral traits (particularly IQ).
<br>
In addition, we briefly considered the 2002 paper <a href="https://doi.org/10.1126/science.1078311" target="_blank" rel="noopener noreferrer" title="Genetic structure of human populations">_Genetic Structure of Human Populations_</a> by Noah Rosenberg et al., which was the most cited paper in Science in its year of publication, and which continues to be cited in scientific and philosophical debates until the present day. Our main aim, however, was not to discuss its scientific findings, but to discuss why this paper has repeatedly been cited as evidence for a biological basis to race by looking at the paper <a href="http://dx.doi.org/10.3998/ptb.6959004.0009.012" target="_blank" rel="noopener noreferrer" title="Are Clusters Races?">_Are Clusters Races? A Discussion of the Rhetorical Appropriation of Rosenberg et al.'s 'Genetic Structure of Human Populations'_</a> by Melissa Wills, which was published fifteen years later. 
<br>
The first meeting ended with a discussion about how we as researchers can decrease the probability of our research being misappropriated.
<br><br>

You can find the slides (in PDF format) used in connection to this meeting <a href="Slides/ADWG_meeting1_misappropriation_genetics.pdf" target="_blank" rel="noopener noreferrer" title="ADWG meeting - The misappropriation of genetics">here</a>.
<br><br><br>

## Further reading:
<br>

* A brief <a href="https://www.science.org/content/article/it-s-toxic-place-how-online-world-white-nationalists-distorts-population-genetics" target="_blank" rel="noopener noreferrer" title="It's a toxic place">interview with Jedidiah Carlson</a> in Science.
* A <a href="https://www.nature.com/articles/d41586-022-03252-z" target="_blank" rel="noopener noreferrer" title="Counter the weaponization of genetics research by extremists">comment by Carlson et al.</a> published in Nature in October 2022.
* <a href="https://doi.org/10.1126/science.abm7530" target="_blank" rel="noopener noreferrer" title="Getting genetic ancestry right for science and society">_Getting genetic ancestry right for science and society_</a> by Anna C.F. Lewis et al., published in Science in April 2022.
<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```