---
title: "Movies"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## About the troubling history and legacy of eugenics 
<br>
<a href="https://www.dr.dk/drtv/episode/de-aandssvages-historie_-de-ustyrlige_113803" target="_blank" rel="noopener noreferrer" title="De aandsvages historie: De ustyrlige">_De aandsvages historie: De ustyrlige_</a>, a DR series (only in Danish)
<br><br>
<a href="https://www.imdb.com/title/tt5686132/" target="_blank" rel="noopener noreferrer" title="The Immortal Life of Henrietta Lacks">_The Immortal Life of Henrietta Lacks_</a>, an HBO movie from 2017.
<br><br><br>

## About gene editing 
<br>
<a href="https://www.imdb.com/title/tt9612680/" target="_blank" rel="noopener noreferrer" title="Human Nature">_Human Nature_</a>, a Documentary about CRISPR from 2019.
<br><br>
<a href="https://www.netflix.com/dk-en/title/80208910" target="_blank" rel="noopener noreferrer" title="Netflix's Unnatural selection">_Unnatural selection_</a>, a Netflix Documentary from 2019.
<br><br>
<a href="https://www.imdb.com/title/tt0119177/" target="_blank" rel="noopener noreferrer" title="GATTACA">_GATTACA_</a>, a science fiction thriller drama from 1997.
<br><br>
<a href="https://www.imdb.com/title/tt0083658/" target="_blank" rel="noopener noreferrer" title="Blade Runner">_Blade Runner_</a>, a science fiction film from 1982.
<br><br>
<a href="https://www.imdb.com/title/tt0387808/" target="_blank" rel="noopener noreferrer" title="Idiocracy">_Idiocracy_</a>, a science fiction comedy from 2006.
<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```