---
title: "7th meeting - Thursday 25th of January 2023"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## Discrimination and diversity in the Danish research community
<br>
In the first anti-discrimination working group meeting in 2024, we discussed discrimination and diversity in the Danish research community, intersectionalism, and how to be a better ally.
<br><br>

#### What is diversity?

Using the definition presented in the paper <a href="https://doi.org/10.1038/s41557-020-0529-x" target="_blank" rel="noopener noreferrer" title="A diverse view of science to catalyse change">_A diverse view of science to catalyse change_</a> by Urbina-Blanco et al. : 
<br><br>
The ways in which people differ, encompassing all the characteristics that make one individual or group distinctive. The dimensions of diversity include, but are not limited to 
(i) ethnic or national origins, skin colour or nationality, 
(ii) gender, gender identity and gender expression, 
(iii) sexual orientation, 
(iv) background (socio-economic status, immigration status or class), 
(v) religion or belief (including absence of belief), 
(vi) civil or marital status, 
(vii) pregnancy and maternity, paternity, parental leave and 
(viii) age and 
(ix) disability.

<br><br>


#### How to be a better ally!

* Offer diversity and inclusion training and workshops
* Use inclusive communication
* Implement neurodiversity hiring programs
* Use colorblind-friendly pallettes

<br><br><br>

## Further information:
<br>

* <a href="https://doi.org/10.1038/s41557-020-0529-x" target="_blank" rel="noopener noreferrer" title="A diverse view of science to catalyse change">_A diverse view of science to catalyse change_</a>, César A. Urbina-Blanco et al., 2020

<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```