---
title: "Sixth meeting - Wednesday 1st November 2023"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

## Ableism and positive psychology
<br>
In this meeting, the anti-discrimination working group covered ableism, disablism, and positive psychology.

### What is ableism?
<br>
Using the definition presented <a href="https://www.accessliving.org/newsroom/blog/ableism-101/" target="_blank" rel="noopener noreferrer" title="Access living - Ableism 101">here</a>: 
<br>
>_Ableism_ is the __discrimination__ of and __social prejudice__ against people with disabilities based on the belief that __typical abilities__ are __superior__. At its heart, ableism is rooted in the __assumption__ that disabled people require __'fixing'__ and defines people by their disability. Like racism and sexism, ableism classifies entire groups of people as __'less than'__, and includes harmful stereotypes, misconceptions, and generalizations of people with disabilities.

<br><br><br>

### What is disablism?
<br>
Using the definition given <a href="https://www.sense.org.uk/information-and-advice/ableism-and-disablism/" target="_blank" rel="noopener noreferrer" title="Sense - Ableism and disablism">here</a>: 
<br>
> _Disablism_ is a word for __negative__ opinions, behaviour, or abuse against disabled people. You are being disablist if you __treat someone differently__, or choose to __offend__ or __hurt__ someone, because of their disability.

<br><br><br>

### What is the difference between ableism and disablism?
<br>
There is some overlap between _ableism_ and _disablism_, and many people use these two words interchangeably. In general, _ableism_ can be used to describe the way society and people tend to favor able-bodied people, while _disablism_ can be used to describe more direct and conscious acts of discrimination or abuse against people with disabilities. 
<br>
_Disablism_ is a newer word, and it is preferred by some activists because they believe that the word _disablism_ makes it clearer that it has nothing to do with the disabled individual's 'ability'. 
<br><br>
For more information visit the website on ableism and disablism provided by the charity <a href="https://www.sense.org.uk/information-and-advice/ableism-and-disablism/" target="_blank" rel="noopener noreferrer" title="Sense - Ableism and disablism">Sense</a>, or the website about ableism provided by <a href="https://www.accessliving.org/newsroom/blog/ableism-101/" target="_blank" rel="noopener noreferrer" title="Access living - Ableism 101">Access Living</a>. 


You can find the slides (in PDF format) used in connection to this meeting <a href="Slides/ADWG_meeting6_ableism.pdf" target="_blank" rel="noopener noreferrer" title="ADWG meeting - Ableism and positive psychology">here</a>.
<br><br><br>

## Further information:
<br>
https://www.apa.org/ed/precollege/psychology-teacher-network/introductory-psychology/ableism-negative-reactions-disability

https://www-taylorfrancis-com.ez.statsbiblioteket.dk/books/edit/10.4324/9781315623924/understanding-lived-experiences-persons-disabilities-nine-countries-julie-beadle-brown-mario-biggeri-rune-halvorsen-bj%C3%B8rn-hvinden-jan-t%C3%B8ssebro-anne-waldschmidt

https://global.oup.com/academic/product/understanding-the-experience-of-disability-9780190848088?cc=dk&lang=en&#

https://bcrw.barnard.edu/no-body-is-disposable-series/

https://hbr.org/2020/12/why-you-need-to-stop-using-these-words-and-phrases

https://ncdj.org/style-guide/

https://www.bbc.com/worklife/article/20210330-the-harmful-ableist-language-you-unknowingly-use

https://www.autistichoya.com/p/ableist-words-and-terms-to-avoid.html

https://doi.org/10.3389%2Ffpsyg.2021.790506

<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```