---
title: "9th meeting - Thursday 16th of May 2024"
---

```{r, echo=FALSE}
htmltools::includeCSS("./css/footer.css")
```

```{js, echo=FALSE}
$(function() {
  $('.main-container').after($('.footer'));
})
```

<!--
 <a href="" target="_blank" rel="noopener noreferrer" title=""></a>
-->
## Research without participant consent and involvement; is it sustainable?
<br>
In the next anti-discrimination working group meeting we will discuss whether research without participant consent and involvement is sustainable.
<br>
 
<br><br>

<!--
You can find the slides (in PDF format) used in connection to this meeting <a href="Slides/ADWG_meeting.pdf" target="_blank" rel="noopener noreferrer" title="ADWG meeting - ">here</a>.
-->
<br><br><br>

## Further information:
<br>

* <a href=https://www.dr.dk/nyheder/indland/vil-danskere-melde-sig-ud-af-forskning-efter-blodproevesag-ekspert-kalder-det-en" target="_blank" rel="noopener noreferrer" title="SSI and their blood samples">__Vil danskere melde sig ud af forskning efter blodprøvesag? Ekspert kalder det en 'potentiel bombe'__</a>, news article by Jonas Deiborg and Astrid Fischer.

<br><br><br>

```{r, echo=FALSE}
htmltools::includeHTML("include_footer.html")
```